My First Markdown Assignment for July 2015
---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---


## Loading and preprocessing the data
```{r}
unzip("activity.zip") # Unzip archive
data=read.csv("activity.csv")
data$date <-as.Date(data$date, "%Y-%m-%d")

```




## What is mean total number of steps taken per day?
```{r}
q <- mean(data$steps,na.rm=TRUE)
d <- median(data$steps,na.rm=TRUE)

```

The mean total number of steps taken per day is `r q`. The median is `r d`.

## The Histogram showing the total number of steps
```{r}
hist(tapply(data$steps,data$date,sum,na.rm=TRUE),xlab="Total number of steps per day",main=NULL,col="wheat")

```
The histogram to show the average number of steps taken per day.


## Imputing missing values
```{r}
missing <- dim(data[is.na(data$steps),])[1]

```

There are `r missing` rows with missing values.


## Time-series plot

```{r}
# x-axis - Time interval (5, 10, 15, ...)
# y-axis - Average number of steps taken across all days for this time interval

data$date <- strptime(data$date, "%Y-%m-%d")

# Keep a list of all possible days
uniqueDates <- unique(data$dates)
# Keep a list of all possible intervals
uniqueIntervals <- unique(data$interval)

# Split up the data according to the interval
intervalSplit <- split(data$steps, data$interval)

# Find the average amount of steps per time interval - ignore NA values
averageStepsPerInterval <- sapply(intervalSplit, mean, na.rm=TRUE)

# Plot the time-series graph
plot(uniqueIntervals, averageStepsPerInterval, type="l",
     main="Average number of steps per interval across all days", 
     xlab="Interval", ylab="Average # of steps across all days", 
     lwd=2, col="blue")



```


## Are there differences in activity patterns between weekdays and weekends?

```{r}
# Find the location of where the maximum is
#maxIntervalDays <- max(averageStepsPerInterval, na.rm=TRUE)
#maxIndex <- as.numeric(which(averageStepsPerInterval == maxIntervalDays))

# Plot a vertical line where the max is
#maxInterval <- uniqueIntervals[maxIndex]
#abline(v=maxInterval, col="red", lwd=3)

```


